---
title: Data Clean Up & Prep for Shiny App
output:
  html_document:
---

## Setup
```{r Setup}

library(ggplot2)
library(plotly)
library(tidyverse)
library(scales) # for viz
library(RColorBrewer) # for viz

# For spatial work
library(sf)
library(mapview) # plotting
library(leafpop) # for customizing popups on maps
library(leaflet)
```


## Read in Data: CDPR
```{r Read in Data: CDPR}

# Cu for all crops for 1990-2006
cdpr1 <- read_csv("D:/LocalRepos/CDPR-Copper_ExternalData/CalPIP_Cu_1990-2006.csv")

# Cu for all crops for 2007
cdpr2 <- read_csv("D:/LocalRepos/CDPR-Copper_ExternalData/CalPIP_Cu_2007.csv")

# All crops for 2008-2021
cdpr3 <- read_csv("D:/LocalRepos/CDPR-Copper_ExternalData/CalPIP_Cu_2008-2021.csv")

# Bind them all together
cdpr <- bind_rows(cdpr1, cdpr2, cdpr3)

rm(cdpr1, cdpr2, cdpr3)
```


## CDPR Data Clean-up: 
### Clean up SITES and Columns
```{r CDPR: Keep Any Ag SITES and Keep ONLY rice SITES}

# Counts of site types
sites <- cdpr %>% count(SITE_NAME)

# create df with ag-related SITE only, including any outdoor-related plant production
allCu <- cdpr %>% 
  filter(SITE_NAME != "" & 
           SITE_NAME != "AIRPORTS AND LANDING FIELDS (RUNWAYS, ETC.)" & 
           SITE_NAME != "ANIMAL HUSBANDRY PREMISES" & 
           SITE_NAME != "ANTIFOULING TREATMENT SITES (ALL OR UNSPEC)" & 
           SITE_NAME != "AQUATIC AREAS, WATER AREAS (ALL OR UNSPEC)" & 
           SITE_NAME != "AQUATIC SITE - HUMAN/ANIMAL USE (COMBINED SITE)" &
           SITE_NAME != "AQUATIC SITE - INDUSTRIAL USE (COMBINED SITE)" & 
           SITE_NAME != "BUILDINGS AND STRUCTURES (NON-AG OUTDOOR)" & 
           SITE_NAME != "CANNABIS (ALL OR UNSPECIFIED)" &
           SITE_NAME != "COMMERCIAL, INSTITUTIONAL OR INDUSTRIAL AREAS" &
           SITE_NAME != "COMMODITY FUMIGATION" & 
           SITE_NAME != "COUNTY AG. COMM. SALES" & 
           SITE_NAME != "FUMIGATION, OTHER" & 
           SITE_NAME != "GREENHOUSES (EMPTY) (ENVIRONS, BENCHES, ETC.)" & 
           SITE_NAME != "HUMAN DRINKING WATER SYSTEMS (POTABLE)" & 
           SITE_NAME != "INDUSTRIAL PROCESSING WATER" & 
           SITE_NAME != "INDUSTRIAL WASTE DISPOSAL SYSTEMS, DISPOSAL WATER" & 
           SITE_NAME != "IRRIGATION SYSTEMS (DITCHES, CANAL BANKS, ETC.)" & 
           SITE_NAME != "LANDSCAPE MAINTENANCE" & 
           SITE_NAME != "N-GRNHS GRWN CUT FLWRS OR GREENS" & 
           SITE_NAME != "N-GRNHS GRWN PLANTS IN CONTAINERS" & 
           SITE_NAME != "N-GRNHS GRWN TRNSPLNT/PRPGTV MTRL" & 
           # SITE_NAME != "N-OUTDR CONTAINER/FLD GRWN PLANTS" & 
           # SITE_NAME != "N-OUTDR GRWN CUT FLWRS OR GREENS" & 
           # SITE_NAME != "N-OUTDR GRWN TRNSPLNT/PRPGTV MTRL " & 
           SITE_NAME != "ORNAMENTAL TURF (ALL OR UNSPEC)" & 
           SITE_NAME != "PUBLIC HEALTH PEST CONTROL" & 
           SITE_NAME != "RECREATIONAL AREAS, TENNIS COURTS, PARKS, ETC." & 
           SITE_NAME != "REGULATORY PEST CONTROL" & 
           SITE_NAME != "RESEARCH COMMODITY" & 
           SITE_NAME != "RIGHTS OF WAY" & 
           # SITE_NAME != "SOIL APPLICATION, PREPLANT-OUTDOOR (SEEDBEDS,ETC.)" & 
           SITE_NAME != "STRUCTURAL PEST CONTROL" & 
           SITE_NAME != "SWIMMING POOL WATER SYSTEMS (POOLS, SPAS, ETC.)" & 
           SITE_NAME != "TURF, GOLF COURSE (FAIRWAYS, GREENS, ROUGH)" & 
           # SITE_NAME != "UNCULTIVATED AGRICULTURAL AREAS (ALL OR UNSPEC)" & 
           SITE_NAME != "UNCULTIVATED NON-AG AREAS (ALL OR UNSPEC)" & 
           SITE_NAME != "URBAN AREAS (ALL OR UNSPEC) (RESIDENTIAL, ETC.)" & 
           SITE_NAME != "VERTEBRATE PEST CONTROL" & 
           SITE_NAME != "WOOD PROTECTION TREATMENTS (ALL OR UNSPECIFIED)")


# Remove unnecessary columns
allCu <- allCu[,-c(1, 3)]

# Remove NA, blank values.
# sum(is.na(allCu$POUNDS_CHEMICAL_APPLIED))
# sum(is.na(allCu$APPLICATION_MONTH))
# sum(allCu$POUNDS_CHEMICAL_APPLIED == "")
# sum(allCu$APPLICATION_MONTH == "")

allCu <- allCu %>%
  filter(!is.na(POUNDS_CHEMICAL_APPLIED)) %>%
  filter(!is.na(APPLICATION_MONTH))

```


### Clean Column Info
```{r Clean column info}

# Quick column clean-up
allCu$APPLICATION_MONTH <- factor(str_to_title(allCu$APPLICATION_MONTH),
                                  levels = c("January", "February", "March", "April", "May", "June", 
                                             "July", "August", "September", "October", "November", "December"))
allCu$COUNTY_NAME <- factor(str_to_title(allCu$COUNTY_NAME))
allCu$CHEMICAL_NAME <- factor(str_to_title(allCu$CHEMICAL_NAME))
allCu$SITE_NAME <- factor(str_to_title(allCu$SITE_NAME))
allCu$PRODUCT_NAME <- factor(str_to_title(allCu$PRODUCT_NAME))

# Convert pounds to kilograms
allCu <- allCu %>%
  mutate(KG_CHEMICAL_APPLIED = POUNDS_CHEMICAL_APPLIED*0.4535924,
         .after = POUNDS_CHEMICAL_APPLIED)

# Convert pounds chemical to pounds copper
# Create table of all chemicals used, then found conversions online
# Decided not to do this, because there are too many chemicals that have 'fuzzy' names and I cannot trace all of them accurately.  So, I will just plot kg of copper-based chemical applied

```


## Preparing for Mapping
### Split COMTRS into matching columns in PLSS df
```{r Split COMTRS}

# COMTRS stands for: county/meridian/township/range/section
# Non-ag pesticide use reports do not have this because they are reported at county level only.

# Digits 1&2 are county, 3rd = meridian, 4-6 = Township (xxN, xxS), 7-9 = Range (xxE, xxW), 10-11 = Section
# To match PLSS spatial data, start all townships with "T", all ranges with "R", and abbreviate meridians as "HM", "MDM", "SBM", where "HM" = Humboldt, "MDM" = Mount Diablo, and "SBM" = San Bernardino
# So convert from CDPR to PLSS as meridan of: "H" --> "HM", "M" --> "MDM", & "S" --> "SBM"


allCu <- allCu %>%
  mutate(County_Num = str_sub(COMTRS, start = 1, end = 2),
         Meridian = str_sub(COMTRS, start = 3, end = 3),
         Township = str_sub(COMTRS, start = 4, end = 6),
         Range = str_sub(COMTRS, start = 7, end = 9),
         Section = str_sub(COMTRS, start = 10, end = 11))

# Further conversion to match PLSS (separated from above for clarity)
# Create a "TownshipRa" column as well
allCu <- allCu %>%
  mutate(Meridian = case_when(Meridian == "H" ~ "HM",
                              Meridian == "M" ~ "MDM",
                              Meridian == "S" ~ "SBM"),
         # Township = str_c("T", Township),
         # Range = str_c("R", Range),
         TownshipRa = str_c(Township, Range, sep = " "))


# Creating NA data for every township/range and County is actually not necessary because by leaving these township-range values as "NA", they will be plotted as grey, rather than as a light orange as part of the palette because they would be seen as 0.  Visually, having the NA (i.e., 0) values as grey helps the township-ranges with actual values to stand out better.
```


## Write CDPR data to R object
Like the PLSS spatial data below, this single file to too big to place on GitHub.  Thus, after all of the cleaning and organization steps above, I'm splitting them into smaller datasets to save, then I'll re-bind them at the beginning of the code for the ShinyApp.
```{r}

# Split data into smaller sets of 5 years each.
Cu90_94 <- allCu %>%
  filter(YEAR %in% c(1990, 1991, 1992, 1993, 1994))
Cu95_99 <- allCu %>%
  filter(YEAR %in% c(1995, 1996, 1997, 1998, 1999))
Cu00_04 <- allCu %>%
  filter(YEAR %in% c(2000, 2001, 2002, 2003, 2004))
Cu05_09 <- allCu %>%
  filter(YEAR %in% c(2005, 2006, 2007, 2008, 2009))
Cu10_14 <- allCu %>%
  filter(YEAR %in% c(2010, 2011, 2012, 2013, 2014))
Cu15_19 <- allCu %>%
  filter(YEAR %in% c(2015, 2016, 2017, 2018, 2019))
Cu20_21 <- allCu %>%
  filter(YEAR %in% c(2020, 2021))


write_rds(x = Cu90_94, file = "./Data/CleanData/CDPRAppData/CDPRCu90_94.rds")
write_rds(x = Cu95_99, file = "./Data/CleanData/CDPRAppData/CDPRCu95_99.rds")
write_rds(x = Cu00_04, file = "./Data/CleanData/CDPRAppData/CDPRCu00_04.rds")
write_rds(x = Cu05_09, file = "./Data/CleanData/CDPRAppData/CDPRCu05_09.rds")
write_rds(x = Cu10_14, file = "./Data/CleanData/CDPRAppData/CDPRCu10_14.rds")
write_rds(x = Cu15_19, file = "./Data/CleanData/CDPRAppData/CDPRCu15_19.rds")
write_rds(x = Cu20_21, file = "./Data/CleanData/CDPRAppData/CDPRCu20_21.rds")

```


## Read in and Prep Spatial PLSS data
### Read in PLSS data, join geometries by County & TownshipRa
```{r PLSS data}

# This spatial dataset is better, because it includes county names and numbers already
plss <- st_read("D:/LocalRepos/CDPR-Copper/Data/Spatial/Statewide_CA_PLSS_NAD83AlbersCA/Statewide_CA_PLSS_NAD83AlbersCA.shp")

str(plss)
summary(plss)

# check geometry type
# object type is MULTIPOLYGON
# The 18 levels are the possible object types that it could be
# st_geometry_type(plss)
# plss[1]


# check CRS of the file data
# See that it is in NAD83 / California Albers
# st_crs(plss)

# To get extent of the file
# gives furthest N, S, E, W edges of the data
# st_bbox(plss)

# View all metadata and attributes, print to screen
# plss
# Or the first row
# plss[1,9]

# To plot, need to use geom_sf and coord_sf
# Note, this is MUCH FASTER than plot(plss) or using ggplot without geom_sf & coord_sf
# ggplotly(
# ggplot() +
#   geom_sf(data = plss_co) +
#   theme_bw() +
#   coord_sf()
# )

# View contents of a specific column, here just unique values
# unique(plss$TOWNSHIP)


# Group geometries by county
plss_co <- plss %>%
  group_by(NAME) %>%
  summarize(geometry = st_union(geometry))

# Group geometries by TownshipRange
plss_tr <- plss %>%
  mutate(TownshipRa = str_c(TOWNSHIP, RANGE, sep = " ")) %>%
  group_by(NAME, TownshipRa) %>%
  summarize(geometry = st_union(geometry))

# Quick plots to check
# plot(plss_co)
# plot(plss_tr)
```


### Merge allCu data to plss spatial data
This is to merge the yearly summed application totals of all copper-based pesticides to the spatial plss data.  The ShinyApp will allow users to plot a map based on yearly sums.  Separately, they'll be able to view plots of the data filtered by different factors such as county, month, product name, chemical name, and crop application.
Due to file size limits on GitHub, need to save each yearly plss object separately.  In the Shiny App, the years can then be merged as a single plss object.
```{r Merging rice data to plss}

# First need to summarize POUNDS_CHEMICAL_APPLIED and KG_CHEMICAL_APPLIED by year and Township
allCu_sum_tr <- allCu %>%
  drop_na(Meridian) %>%
  group_by(YEAR, COUNTY_NAME, TownshipRa) %>%
  summarise(sum_kg_applied = sum(KG_CHEMICAL_APPLIED))

# Change TownshipRa 12S 31E to 12S 21E.  This was likely a typo, because it says that there was 1 application on peaches, but it is clear from the map that this is very mountainous terrain and is actually part of Kings Canyon NP.  I'm assuming that this was a typo, and instead of 31E it should be 21E, where there actually is farmland.
allCu_sum_tr$TownshipRa[allCu_sum_tr$TownshipRa == "12S 31E"] <- "12S 21E"


# Joined datasets year by year (need to because requires replacing NA values of Year due to applications not being made in every township)
plss_allCu_tr1990 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1990, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1990))

plss_allCu_tr1991 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1991, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1991))

plss_allCu_tr1992 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1992, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1992))

plss_allCu_tr1993 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1993, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1993))

plss_allCu_tr1994 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1994, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1994))

plss_allCu_tr1995 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1995, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1995))

plss_allCu_tr1996 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1996, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1996))

plss_allCu_tr1997 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1997, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1997))

plss_allCu_tr1998 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1998, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1998))

plss_allCu_tr1999 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 1999, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 1999))

plss_allCu_tr2000 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2000, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2000))

plss_allCu_tr2001 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2001, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2001))

plss_allCu_tr2002 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2002, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2002))

plss_allCu_tr2003 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2003, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2003))

plss_allCu_tr2004 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2004, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2004))

plss_allCu_tr2005 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2005, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2005))

plss_allCu_tr2006 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2006, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2006))

plss_allCu_tr2007 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2007, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2007))

plss_allCu_tr2008 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2008, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2008))

plss_allCu_tr2009 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2009, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2009))

plss_allCu_tr2010 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2010, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2010))

plss_allCu_tr2011 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2011, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2011))

plss_allCu_tr2012 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2012, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2012))

plss_allCu_tr2013 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2013, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2013))

plss_allCu_tr2014 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2014, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2014))

plss_allCu_tr2015 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2015, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2015))

plss_allCu_tr2016 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2016, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2016))

plss_allCu_tr2017 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2017, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2017))

plss_allCu_tr2018 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2018, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2018))

plss_allCu_tr2019 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2019, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2019))

plss_allCu_tr2020 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2020, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2020))

plss_allCu_tr2021 <- left_join(x = plss_tr, 
                              y = allCu_sum_tr[allCu_sum_tr$YEAR == 2021, ], 
                              by = c("TownshipRa" = "TownshipRa", "NAME" = "COUNTY_NAME")) %>%
  replace_na(list(YEAR = 2021))


#### DELETE THIS #####
# Create a single plss with all years' data combined 
plss_allCu_tr_all <- bind_rows(plss_allCu_tr1990, plss_allCu_tr1991, plss_allCu_tr1992, plss_allCu_tr1993,
                               plss_allCu_tr1994, plss_allCu_tr1995, plss_allCu_tr1996, plss_allCu_tr1997,
                               plss_allCu_tr1998, plss_allCu_tr1999, plss_allCu_tr2000, plss_allCu_tr2001,
                               plss_allCu_tr2002, plss_allCu_tr2003, plss_allCu_tr2004, plss_allCu_tr2005,
                               plss_allCu_tr2006, plss_allCu_tr2007, plss_allCu_tr2008, plss_allCu_tr2009,
                               plss_allCu_tr2010, plss_allCu_tr2011, plss_allCu_tr2012, plss_allCu_tr2013,
                               plss_allCu_tr2014, plss_allCu_tr2015, plss_allCu_tr2016, plss_allCu_tr2017,
                               plss_allCu_tr2018, plss_allCu_tr2019, plss_allCu_tr2020, plss_allCu_tr2021)

# remove year-based plss objects to save memory
# rm(plss_allCu_tr1990, plss_allCu_tr1991, plss_allCu_tr1992, plss_allCu_tr1993, plss_allCu_tr1994, plss_allCu_tr1995,
#    plss_allCu_tr1996, plss_allCu_tr1997, plss_allCu_tr1998, plss_allCu_tr1999, plss_allCu_tr2000, plss_allCu_tr2001,
#    plss_allCu_tr2002, plss_allCu_tr2003, plss_allCu_tr2004, plss_allCu_tr2005, plss_allCu_tr2006, plss_allCu_tr2007,
#    plss_allCu_tr2008, plss_allCu_tr2009, plss_allCu_tr2010, plss_allCu_tr2011, plss_allCu_tr2012, plss_allCu_tr2013, 
#    plss_allCu_tr2014, plss_allCu_tr2015, plss_allCu_tr2016, plss_allCu_tr2017, plss_allCu_tr2018, plss_allCu_tr2019,
#    plss_allCu_tr2020, plss_allCu_tr2021)

##### TO HERE #####


##### EVENTUALLY DELETE THIS TOO #####
# Test to print just one year of data
ggplot() +
  geom_sf(data = plss_allCu_tr_all[plss_allCu_tr_all$YEAR == 2021,], 
          aes(geometry = geometry, fill = sum_kg_applied)) + 
  theme_bw() + 
  coord_sf() +
  # facet_wrap(~YEAR) +
  scale_fill_distiller(name = "Total Kilograms",
                     labels = comma,
                     trans = "reverse",
                     palette = "Oranges")

# Plot when using just 2021 dataframe
# library(extrafont)
# library(extrafontdb)
# font_import()   # Run once
# loadfonts(device = "win")

# To get the degree symbol to work: Tools -> Graphics -> Backend -> Cairo

```

## Write spatial plss data to R objects
```{r}
# PLSS County-level spatial data, no associated copper application data
write_rds(x = plss_co, file = "./Data/CleanData/plssCounty.rds")

# PLSS Township-Range level spatial data, no associated copper application data
write_rds(x = plss_tr, file = "./Data/CleanData/plssTownRa.rds")

# PLSS Township-Range level spatial data, INCLUDES copper application data by year
# one file for each year
write_rds(x = plss_allCu_tr1990, file = "./Data/CleanData/SpatialData/plssTRCu1990.rds")
write_rds(x = plss_allCu_tr1991, file = "./Data/CleanData/SpatialData/plssTRCu1991.rds")
write_rds(x = plss_allCu_tr1992, file = "./Data/CleanData/SpatialData/plssTRCu1992.rds")
write_rds(x = plss_allCu_tr1993, file = "./Data/CleanData/SpatialData/plssTRCu1993.rds")
write_rds(x = plss_allCu_tr1994, file = "./Data/CleanData/SpatialData/plssTRCu1994.rds")
write_rds(x = plss_allCu_tr1995, file = "./Data/CleanData/SpatialData/plssTRCu1995.rds")
write_rds(x = plss_allCu_tr1996, file = "./Data/CleanData/SpatialData/plssTRCu1996.rds")
write_rds(x = plss_allCu_tr1997, file = "./Data/CleanData/SpatialData/plssTRCu1997.rds")
write_rds(x = plss_allCu_tr1998, file = "./Data/CleanData/SpatialData/plssTRCu1998.rds")
write_rds(x = plss_allCu_tr1999, file = "./Data/CleanData/SpatialData/plssTRCu1999.rds")
write_rds(x = plss_allCu_tr2000, file = "./Data/CleanData/SpatialData/plssTRCu2000.rds")
write_rds(x = plss_allCu_tr2001, file = "./Data/CleanData/SpatialData/plssTRCu2001.rds")
write_rds(x = plss_allCu_tr2002, file = "./Data/CleanData/SpatialData/plssTRCu2002.rds")
write_rds(x = plss_allCu_tr2003, file = "./Data/CleanData/SpatialData/plssTRCu2003.rds")
write_rds(x = plss_allCu_tr2004, file = "./Data/CleanData/SpatialData/plssTRCu2004.rds")
write_rds(x = plss_allCu_tr2005, file = "./Data/CleanData/SpatialData/plssTRCu2005.rds")
write_rds(x = plss_allCu_tr2006, file = "./Data/CleanData/SpatialData/plssTRCu2006.rds")
write_rds(x = plss_allCu_tr2007, file = "./Data/CleanData/SpatialData/plssTRCu2007.rds")
write_rds(x = plss_allCu_tr2008, file = "./Data/CleanData/SpatialData/plssTRCu2008.rds")
write_rds(x = plss_allCu_tr2009, file = "./Data/CleanData/SpatialData/plssTRCu2009.rds")
write_rds(x = plss_allCu_tr2010, file = "./Data/CleanData/SpatialData/plssTRCu2010.rds")
write_rds(x = plss_allCu_tr2011, file = "./Data/CleanData/SpatialData/plssTRCu2011.rds")
write_rds(x = plss_allCu_tr2012, file = "./Data/CleanData/SpatialData/plssTRCu2012.rds")
write_rds(x = plss_allCu_tr2013, file = "./Data/CleanData/SpatialData/plssTRCu2013.rds")
write_rds(x = plss_allCu_tr2014, file = "./Data/CleanData/SpatialData/plssTRCu2014.rds")
write_rds(x = plss_allCu_tr2015, file = "./Data/CleanData/SpatialData/plssTRCu2015.rds")
write_rds(x = plss_allCu_tr2016, file = "./Data/CleanData/SpatialData/plssTRCu2016.rds")
write_rds(x = plss_allCu_tr2017, file = "./Data/CleanData/SpatialData/plssTRCu2017.rds")
write_rds(x = plss_allCu_tr2018, file = "./Data/CleanData/SpatialData/plssTRCu2018.rds")
write_rds(x = plss_allCu_tr2019, file = "./Data/CleanData/SpatialData/plssTRCu2019.rds")
write_rds(x = plss_allCu_tr2020, file = "./Data/CleanData/SpatialData/plssTRCu2020.rds")
write_rds(x = plss_allCu_tr2021, file = "./Data/CleanData/SpatialData/plssTRCu2021.rds")

```

